Simulating the Linux page cache in distributed applications with the WRENCH library

### 2020-12-07 paper_io_sim.tex
minor edit in abstract

\begin{document}
\title{I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework}

@@

        The rapid emergence of Big Data seen in recent years has resulted in a 
        growing needs for efficient data storing and optimized data analysis. 
        Despite relying on large computing infrastructures with powerful computing capability 
        to process these large datasets, an I/O bottleneck remains. 
        One widely-used approach to minimize the costs of data transfers during
        regular use is through the employment of the page cache.
        While many simulation tools have been developed to 
        support studies in computing systems optimization, page cache simulation 
        has not been fully captured or remains absent from these simulators. 
        The lack of ability to simulate I/O with page cache leads to inaccurate 
        simulation results in many situations, especially when dealing with data intensive applications.

>>>>

\begin{document}

\title{Simulating the Linux page cache in distributed applications with the WRENCH library}

@@

        The rapid emergence of Big Data seen in recent years has resulted in a 
        growing needs for efficient data storing and optimized data analysis. 
        Despite relying on large computing infrastructures with powerful computing capability 
        to process these large datasets, an I/O bottleneck remains. 
        One widely-used approach to minimize the costs of data transfers during
        regular use is through the employment of the Linux page cache.
        While many simulation tools have been developed to 
        support studies in computing systems optimization, page cache simulation 
        has not been fully captured or remains absent from these simulators. 
        The lack of ability to simulate I/O with page cache leads to inaccurate 
        simulation results in many situations, especially when dealing with data intensive applications.
